### 2016-03-09 paper/algorithm.tex
yasu

\section{Swarm Fusion Method}
{\it Swarm Fusion} (SF) is a natural extension of Fusion Move method
(FM). Take a multi-threading environment to explain our idea, but the
technique is also applicable to other parallel programming model such as
{\it MapReduce} in cloud computing.
%
Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generate a solution proposal
for fusion. We have 1) a {\it proposal pool}, from which we can pick
arbitrary number of proposal generation schemes and generate proposals,
and 2) a {\it solution pool}, from which we can pick arbitrary number of
intermediate solutions generated by all the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread, but the scheme can be more
general.

SF has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
$T_i$), determining the processing flow of the algorithm: In each fusion
step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool.
The bottom right configuration in Figure~\ref{fig:model}

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf}
 \caption{Base Swarm Fusion architecture.}\label{fig:model}
\end{figure}

%
Furthermore, one can also control how to choose proposal generation
schemes and/or solutions from the pools.

>>>>

\section{Multi-way particle swarm fusion}
Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
method (FM). We call our method Swarm Fusion (SF) in short. Take a
multi-threading environment to explain our idea, while the technique is
also applicable to other parallel programming model such as {\it
MapReduce} in cloud computing.
%

Assume that we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generate a solution proposal
for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we can pick
arbitrary number of proposal generation schemes and generate proposals,
and 2) a {\it solution pool}, from which we can pick arbitrary number of
intermediate solutions generated by all the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread, but the scheme can be more
general.

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
$T_i$), determining the processing flow of the algorithm: In each fusion
step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool.
%
One can further customize how to pick certain proposal generation
schemes (as in ~\cite{delong}) or solutions. Swarm Fusion framework is
very flexible and yields various architecture as shown in
Figure~\ref{fig:model}.
%
The bottom right configuration is the most general one, in which we
always fuse some solution proposals and some concurrent solutions. This
is a multi-way fusion (not binary) with a non-submodular energy, and we
use TRW~\cite{kolmogorov} for the fusion. Of course, if one knows that a
certain fusion step is a binary fusion with submodular energy, one can
use graph-cuts instead~\cite{alpha_expansion_paper}. If a certain fusion
step is a binary fusion with non-submodular energy, one can use
QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the solution pool. The
asynchronous processing could be difficult for cloud parallel computing.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods.
}\label{fig:model}
\end{figure}
%
%

%

\mysubsubsubsection{Relationships to existing methods}

\noindent
abc
